Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2017-12-17 paper/paper.Rmd
done with image characteristics

```{r Image-Characteristics-Table, fig.cap ="\\label{tab:Image-Characteristics-Table}"}
ImageCharacteristics <- amin %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
ImageCharacteristics<-ImageCharacteristics[1:5,]
knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=FALSE, format.args=list(width=8), caption="Combinations of image attibutes that are most common in the image set. The combination of the Logo Wall background and the Level angle are shared by three of the five image combinations.", format = "latex")
```

@@

There were several characteristics of the image recorded during manual tagging, as listed in Table \@ref(tab:Scene-Attributes-Table). This section examines the prevalence of these characteristics in the data collection. Figure \@ref(fig:ICFigs) shows the relationships of a subset of characteristics, using mosaic plots.

The characteristics of the images were recorded in the manual tagging process and there are uneven amounts of faces with certain image attributes. These relationships can be explored in mosaics for the images that were all considered manually. The scene information was tallied and the combinations of these features were compared to how many potential faces were found with the combination of scene attributes.

This showed that crowd members faces were often recognized which is helpful as it shows a strong ability of Google's algorithm to recognize faces, even when these faces are not the goal of the research. It also allowed for an increase in understanding how attributes of a face or image impact on the API detection.

The colors in the mosaic \@ref(fig:ICFigs) (a) in Figure \@ref(fig:ICFigs) show the proportion of faces that matched those found manually, given the angle the faces were captured from. There is a greater proportion of API faces that matched the faces found manually than those that did not match. However given the face was captured from a birds eye angle there were a lot less faces proportionally that matched those found manually. The most common faces in the set were those captured level to player's faces, these faces were often recognized by the APIs as well.

@@

Figure \@ref(fig:ICFigs) (c) contains a mosaic which allows consideration of the interaction between two image attributes. It can be seen that the background being the logo wall and the angle of level is common to the highest amount of faces. There are also no images that were taken at an upward angle with the background of the court.

This mosaic, Figure \@ref(fig:ICFigs) (d), allows consideration of the interaction between the background of the image captured and the situation that could possibly be occurring. As seen previously, the logo wall is the most common background, but it is never the background of an image of the crowd. The court is the background of an image only when players are captured, this occurs during close ups and while the court is in play.

## Accessories

>>>>

```{r Image-Characteristics-Table, fig.cap ="\\label{tab:Image-Characteristics-Table}"}
ImageCharacteristics <- amin %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
ImageCharacteristics<-ImageCharacteristics[1:5,]
knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=FALSE, format.args=list(width=8), caption="Top five most frequent image attribute combinations.", format = "latex")
```

@@

Image characteristics (Table \@ref(tab:Scene-Attributes-Table)) were constructed during manual tagging. The scene information was tallied and the most common combinations of these features shown in Table \@ref(tab:Image-Characteristics-Table).

Figure \@ref(fig:ICFigs) examines the relationships between several of the image characteristics, and face detection by the Google API, using mosaic plots. Plot (a) compares the angle of capture by detection rate. Colour is mapped to detection. Most images were taken at a level angle. The highest capture rate occurred when the angle was level, and least with a bird's eye, as might be expected. Plot (b) compares the situation with face detection. Close-up was the most common situation. The detection rate was the same across situations.

@@

Plots (c) and (d) show the three way relationship between capture angle, situation, background and face detection. In the level capture angle most faces were detected against the logo wall, but with bird's eye most were captured against the court. In close-ups the most faces were detected against the logo wall.

## Player accessories
